### 2012-12-27 inst/examples/sensitivity.Rmd
small noise example

```{r sdp-pars-fixed}
profit = function(x,h) pmin(x, h)
delta <- 0.01
OptTime = 20  # stationarity with unstable models is tricky thing
reward = 0
xT <- 0
z_g = function() rlnorm(1, 0, sigma_g)
z_m = function() 1+(2*runif(1, 0,  1)-1) * sigma_m
```

@@

```{r sdp-pars-explore}
sigma_g <- 0.1
sigma_m <- 0.0
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

@@

```{r parallel, message=FALSE, warning=FALSE, results='hide'}
require(snowfall)
sfInit(par=TRUE, cpu=8)
sfExportAll()
sfLibrary(pdgControl)
sfLibrary(nonparametricbayes)
sfLibrary(reshape2)
sfLibrary(ggplot2)
sfLibrary(data.table)
sfLibrary(tgp)
sfLibrary(kernlab)
sfLibrary(MCMCpack)
sfLibrary(plyr)
```

```{r }
seed <- round(runif(32) * 1e6)
seed[1] <- 1
seed
yields <- lapply(seed, 
function(seed_i){
  Xo <- K # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, seed = seed_i)
  alt <- par_est(obs)
  est <- par_est_allee(obs, f, p)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
#  posteriors_plot(gp, priors) # needs trace=TRUE!
  OPT <- optimal_policy(gp, f, est$f, alt$f,
                        p, est$p, alt$p,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g, alt$sigma_g, 
                        delta, xT, profit, reward, OptTime)
  plot_policies(x_grid, OPT$gp_D, OPT$est_D, OPT$true_D, OPT$alt_D)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
})
```

>>>>

```{r sdp-pars-fixed}
profit = function(x,h) pmin(x, h)
delta <- 0.01
OptTime = 50  # stationarity with unstable models is tricky thing
reward = 0
xT <- 0
z_g = function() rlnorm(1, 0, sigma_g)
z_m = function() 1+(2*runif(1, 0,  1)-1) * sigma_m
```

@@

```{r sdp-pars-explore}
sigma_g <- 0.05
sigma_m <- 0.0
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

@@

```{r }
seed <- round(runif(32) * 1e6)
seed[1] <- 1
seed
yields <- lapply(seed, 
function(seed_i){
  Xo <- K # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=35, nz= 1, 
                 harvest = sort(rep(seq(0, .5, length=7), 5)), seed = seed_i)

  alt <- par_est(obs,  init = c(r=1.5, K=mean(obs$x), s=1))
  est <- par_est_allee(obs, f, p,  init = c(p[1]+1, p[2]-1, p[3]-2, 
                                   s = sigma_g + abs(rnorm(1,0,.1))))

  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)

#  posteriors_plot(gp, priors) # needs trace=TRUE!

  OPT <- optimal_policy(gp, f, est$f, alt$f,
                        p, est$p, alt$p,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g, alt$sigma_g, 
                        delta, xT, profit, reward, OptTime)
  plot_policies(x_grid, OPT$gp_D, OPT$est_D, OPT$true_D, OPT$alt_D)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
})
```
